Homework

### 2016-07-05 Macro Impacts Revised.tex
Mistakes were made: they need fixing.
I calculated the propagated energy and it was larger than the total
initial energy. Clearly mistakes were made that cannot be accounted for
by the neglect of the nonlinear regime. These mistakes must be fixed!

The energy in the longest modes is, for $h\gg\lambda_0$

@@

>>>>

The energy in the longest modes is, for $h\gg\lambda_0\gg r_0$

@@

One source suggests that Earth reacts elastically when the acceleration $\ddot u$ is bounded by $4\te{ms}^{-2}$. Observe,
U(\vec k)=\I\f{P(\vec k)}{K}\f{\vec k}{k^2}\,,
hence
\ddot U(\vec k)=-\I\alpha^2\f{P(\vec k)}{K}\vec k\,.
The inverse transform yields
\ddot u&=-\f{\alpha^2}{K}\nabla p\,.
For our case, within the shock front
\ddot u&=-\f{\alpha^2}{K}\bar p\f{2r-r_0}{r\Delta r}\,.
This function is monotonic increasing, and thus has maximum absolute value
\ddot u_{\te{max}}&=\f{\alpha^2}{K}\bar p\f{2\Delta r+r_0}{(\Delta r+r_0)\Delta r}\,.
We have $r_0$ in terms of $\Delta r$, and hence we can solve the system for both. Unfortunately, the numerical results for $r_0$ and $\Delta r$ are huge... roughly $r_0=10^{17}\te{m}$ and $\Delta r=10^5\te{m}$. Moreover, plugging these results in for the energy $E_{\te{prop}}$ yields an enormous number, on the order of $10^{57}\te{J}$. Given that the total energy deposition is $10^{12}$, it is clear that we made a mistake somewhere...
